---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi = 500
)
```

# Diffusion-Limited Aggregation

The `DLA()` R function performs diffusion-limited aggregation (DLA) and outputs
an integer matrix.

[Link to DLA Wikipedia page.](https://en.wikipedia.org/wiki/Diffusion-limited_aggregation)

The core is written in C++, so the `Rcpp` package is required and will be
installed automatically when DLA.R is sourced.

This is a work in progress, so the program may be slow with a large number of
particles.

## Usage

Below is an example of how the `DLA()` function is used. The output is
visualized with the `ComplexHeatmap` R package.

```{r setup-heatmap, warning=FALSE, message=FALSE}
if (!require("BiocManager", quietly = TRUE, character.only = TRUE)) {
  install.packages("BiocManager", dependencies = TRUE)
}

if (!require("ComplexHeatmap", quietly = TRUE, character.only = TRUE)) {
  BiocManager::install("ComplexHeatmap")
}

library(ComplexHeatmap)
```


```{r DLA-heatmap}
source("DLA.R")

# Dimensions of the output matrix
nr <- 2^8
nc <- 2^8

# The bottom row of the output matrix will be filled with particles to start
x <- seq_len(nc)
y <- rep.int(nr, length(x))
n_particles <- 2^12

res <- DLA(
  nr = nr,
  nc = nc,
  x = x,
  y = y,
  n_particles = n_particles,
  seed = 9001L
)

# Heatmap ----
particle_size <- unit(1.2, "pt")

Heatmap(
  matrix = res,
  col = circlize::colorRamp2(
    breaks = c(
      0L,
      1L,
      quantile(res, 1:4 / 5, na.rm = TRUE),
      max(res, na.rm = TRUE)
    ),
    colors = c("black", "red", "orange", "yellow3", "green2", "blue", "purple")
  ),
  na_col = "grey95",
  cluster_rows = FALSE,
  cluster_columns = FALSE,
  height = particle_size * nr,
  width = particle_size * nc,
  heatmap_legend_param = list(
    title = "Particle\nAggregation\nOrder"
  )
)

```

### Session Information

```{r session-info}
print(sessionInfo(), locale = FALSE)
```

